### 2021-03-28 Chapter-3/Chapter-3.tex
Updates from Overleaf

\chapter{Fast and Precise Side-channel Vulnerability Detection}\label{chapter3}
\section{Problem}
Side-channel attacks infer sensitive information such as cryptographic keys, personal data from software products unconsciously. As we discuss in \S\ref{chapter1} and \S\ref{chapter2}, patching software are usually easier than adopting new hardware to defend against side-channel attacks.

>>>>

\chapter{Fast and Precise Side-channel Vulnerability Detection}\label{chapter3}
\section{Problem}
Side-channel attacks infer sensitive information such as cryptographic keys, personal data from software products unconsciously. Based on the discussions in \S\ref{chapter1} and \S\ref{chapter2}, patching leakage sites in software is usually easier than adopting new hardware to defend against side-channel attacks. In order to eliminate those leakage sites, developers also need to identify potential leakage sites from the code base manually. However, the manual process is tedious and error-prone. Recent studies~\cite{203878} also suggests fixing old vulnerabilities can sometimes introduce new leakages.

Recent work has made good progress in identifying side-channel leakages automatically. Some tools (e.g., DATA, CacheD) have successfully identified unknown leakage sites from software products automatically. However, existing tools have the following limitations.
